Supplementary materials

### 2019-11-05 manuscript/supplemental.Rmd
supplemental figs ready for lynne v1

```{r setup, include=FALSE}
library(here)
library(tidyverse)
library(kableExtra)
```

```{r, include=F}
map <- knitr::include_graphics(here::here("manuscript/figs/map.png"))
field <- read_csv(here::here("data/02_tidied/tidied_field.csv"))
field_photos <- knitr::include_graphics(here::here("manuscript/figs/S3_site_field_photos/field_collage.png"))

map_cap <- "S1. Map showing locations of snow algae sampling locations in summer 2018."
table_cap <- "S2. Table of sample site information of sequenced snow algae samples."
field_photo_cap <- "S3. Photos of snow algae field sites."
```

@@

```{r, fig.cap=map_cap}
map
```

```{r, fig.cap=field_photo_cap}
field_photos
```

```{r}
field %>% 
   filter(have_seq==T) %>% 
   mutate(notes = if_else(sample_id %in% c("pan18.ro","bre18.rd"), "collected from rock",NA_character_)) %>% 
   select(alias, date, elev_m, lat, lon,color_snow, habitat, notes) %>% 
   arrange(date) %>% 
   kable(caption = table_cap) %>% 
   kable_styling(bootstrap_options = "striped")

```

>>>>

```{r setup, include=FALSE}
library(here)
library(tidyverse)
library(kableExtra)
library(knitr)
library(sessioninfo)
```

```{r, include=F}
map <- knitr::include_graphics(here::here("manuscript/figs/map.png"))
field <- read_csv(here::here("data/02_tidied/tidied_field.csv"))
field_photos <- knitr::include_graphics(here::here("manuscript/figs/S3_site_field_photos/field_collage.png"))
micro_photos <- knitr::include_graphics(here::here("manuscript/figs/S4_site_micro_photos/micro.png"))
s18 <- include_graphics(here("manuscript/figs/18s_algae_rel_abund.png"))
tree <- include_graphics(here("manuscript/figs/otu_tree.png"))
tree_taxonomy <- include_graphics(here("manuscript/figs/taxonomy_tree.png"))
diversity <- include_graphics(here("manuscript/figs/diversity.png"))
cellct <- include_graphics(here("manuscript/figs/supp/cellct/cellct.png"))

map_cap <- "S1. Map showing locations of snow algae sampling locations in summer 2018."
table_cap <- "S2. Table of sample site information of sequenced snow algae samples."
field_photo_cap <- "S3. Photos of snow algae field sites."
micro_cap <- "Microphotos of snow algae samples included in sequencing run."
s18_cap <- "Relative abundance barplot of 18S amplicon library"
tree_cap <- "Maximum likelihood tree of rbcL amplicon library. Colors represent OTU assignments."
tax_tree_cap <- "Maximum likelihood tree of rbcL amplicon library. Colors represent taxonomic assignments."
diversity_cap <- "A. Shannon diversity of snow algae samples, plotted against sample elevation. Smooth method = linear model. B. Faith's phylogenetic diversity plotted against sample elevation."
(ref:cellct_cap) "Heatmap showing cell count relative abundance from 117 snow algae samples. Cb = Chlainomonas cf. brevispina, Ck=Chloromonas krienitzii, Cn=Chloromonas cf. nivalis, Cr=Chlainomonas rubra, G=green cells, O=other, Sn=Sanguina nivaloides"
```

@@

```{r, fig.cap=map_cap}
# zoom in
map
```

```{r, fig.cap=field_photo_cap}
# order by date
# sizes the same (crop template)
# arrange in grid
field_photos
```

```{r, fig.cap=micro_cap}
#scale bar
# # sizes the same (crop template)
# arrange in grid
micro_photos
```

```{r s18_rel_abund, fig.cap=s18_cap}
s18 # should this go in the main fig next to the rbcl assignments?
```

```{r tree, fig.cap=tree_cap}
tree
```

```{r tax_tree, fig.cap=tax_tree_cap}
tree_taxonomy
```

```{r, fig.cap=diversity_cap}
diversity
```

```{r, (ref:cellct_cap)}
cellct
```

```{r}
field %>% 
   filter(have_seq==T) %>% 
   mutate(notes = if_else(sample_id %in% c("pan18.ro","bre18.rd"), "collected from rock",NA_character_)) %>% 
   select(alias, date, elev_m, lat, lon,color_snow, habitat, notes) %>% 
   arrange(date) %>% 
   kable(caption = table_cap) %>% 
   kable_styling(bootstrap_options = "striped")
```

```{r}
my_session_info <- sessioninfo::session_info()

my_session_info$platform %>% 
  unlist() %>% 
  enframe() %>% 
  kable(caption = "Session information") %>% 
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = F, position = "left")
```

```{r}
software <- my_session_info$packages %>% 
  as_tibble() %>% 
  select(package, loadedversion) %>% 
  dplyr::rename(version = loadedversion)

# cedar_info <- tibble(package = c(""),
#                      version = c(""))

# software <- software %>% 
#   bind_rows(cedar_info)

software %>% 
  kable(caption=" R software package versions used") %>% 
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = F, position = "left")
```
